Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-04-09 WSSSPE4_report/survey_details.tex
final formatting changes in survey details, new page for references

@@

\begin{figure}[!htb]
    \captionsetup[subfigure]{position=b}
    \centering
    \subcaptionbox{
    The plenary sessions had a good mix of topics and speakers.
    \label{fig:SFig1}
    }{\includegraphics[width=.34\linewidth]{figures/SurveyFig1rev}}
    ~
    \subcaptionbox{
    The balance was right between talks, panels, and lightning talks.
    \label{fig:SFig2}
    }{\includegraphics[width=.32\linewidth]{figures/SurveyFig2rev}}
    ~
    \subcaptionbox{
    There was sufficient time for discussion.
    \label{fig:SFig3}
    }{\includegraphics[width=.25\linewidth]{figures/SurveyFig3rev}}
    \caption{Responses to generate questions about the conference program}
\end{figure}

@@

\noindent \textbf{3. What additional topics would you like to see discussed at the next meeting?}

@@

\noindent \textbf{7. Will you be part of a working group  with colleagues going forward  on a topic addressed at WSSSPE, and if so, which one?}

@@

>>>>

\hspace{0.2cm}

@@

\begin{figure}[!htb]
    \captionsetup[subfigure]{position=b}
    \centering
    \subcaptionbox{
    The plenary sessions had a good mix of topics and speakers.
    \label{fig:SFig1}
    }{\includegraphics[width=.33\linewidth]{figures/SurveyFig1rev}}
    ~
    \subcaptionbox{
    The balance was right between talks, panels, and lightning talks.
    \label{fig:SFig2}
    }{\includegraphics[width=.32\linewidth]{figures/SurveyFig2rev}}
    ~
    \subcaptionbox{
    There was sufficient time for discussion.
    \label{fig:SFig3}
    }{\includegraphics[width=.26\linewidth]{figures/SurveyFig3rev}}
    \caption{Responses to general questions about the conference program}
\end{figure}

@@

\newpage
\noindent \textbf{3. What additional topics would you like to see discussed at the next meeting?}

@@

\newpage
\noindent \textbf{7. Will you be part of a working group  with colleagues going forward  on a topic addressed at WSSSPE, and if so, which one?}

@@

\vspace{0.2cm}

### 2017-04-09 WSSSPE4_report/wg_best_practices_sustainability.tex

Many open source projects for research software document their best practices that contributed to the sustainability of the software.  Many open source projects also document software metrics they use to define their research software project’s success.  This project endeavors to aggregate several sources of these best practices into a consolidated list of best practices, as and to also do the same for software metrics in another consolidated list.  Our team will then create a workflow to evaluate how open source projects stand up to these lists.

@@

The overall objective of the Verify Best Practices and Metrics for Sustainable Software working group is to take the outputs of the WSSSPE efforts to identify best practices for creation of sustainable software for science/academia, and also the outputs of WSSSPE efforts to identify metrics for sustainable software for science/academia and cross-reference these with current open source research software that successfully uses modern software engineering.  This will allow us to identify gaps on both sides.  This approach will also allow the group to  hypothesize how successful open source projects can be further improved, verify that recommended approaches for software engineering for science/academia are sufficient and valid, and that metrics for software engineering for science/academia are relevant and useful.  The group has a specific objective of getting a good cross-sampling of disparate software including community model codes, community cyberinfrastructure, community analytic tools, etc.

@@

\noindent
Resources include research projects suggested from WSSSPE community including:
\begin{itemize}
\item FLASH -- \url{http://flash.uchicago.edu/site/flashcode/}
\item GROMACS -- http://www.gromacs.org/
\item CIG -- \url{http://geodynamics.org/}
\item CUAHSI -- \url{https://www.cuahsi.org/}
\item CSDMS -- \url{https://csdms.colorado.edu/wiki/Main_Page}
\item OntoSoft -- \url{http://www.ontosoft.org/}
\item Anything -- from ASCL (astronomy) \href{https://ui.adsabs.harvard.edu/#search/q=bibstem%3A%22ASCL%22&sort=citation_count%20desc%2C%20bibcode%20desc}{ ASCL entries sorted by citation count}
\item Yt-project -- (astronomy) \url{http://yt-project.org}
\item Einstein Toolkit -- (physics) \url{https://einsteintoolkit.org/}
\item SpEC -- (physics) \url{https://www.black-holes.org/SpEC.html}
\item pyCLOUDY -- (astrophysics) \url{http://ascl.net/1304.020}
\end{itemize}

@@

\begin{itemize}
\item Good Enough Practices in Scientific Computing, Wilson et al. 2016

\begin{itemize}
\item \url{https://swcarpentry.github.io/good-enough-practices-in-scientific-computing/}
\item \url{http://arxiv.org/abs/1609.00037}
\end{itemize}

\item Best Practices for Scientific Computing, Wilson et al. 2014
\begin{itemize}
\item \url{http://dx.doi.org/10.1371/journal.pbio.1001745}
\item 8 high level categories 
\end{itemize}

\item Butterfly: a paradigm towards stable bio & neuro informatics tools development
\begin{itemize}
\item \url{http://www.frontiersin.org/10.3389/conf.fnins.2015.91.00009/event_abstract}
\end{itemize}

\item Working towards Sustainable Software for Science: Practice and Experiences
\begin{itemize}
\item JORS collection
\item \url{http://openresearchsoftware.metajnl.com/collections/special/working-towards-sustainable-software-for-science/}
\end{itemize}

@@

\item Best Practices for Scientific Computing
\begin{itemize}
\item \url{http://arxiv.org/abs/1210.0530v1}
\end{itemize}

@@

\item WSSSPE papers from past WSSSPE workshops
\begin{itemize}
\item \url{http://wssspe.researchcomputing.org.uk/}
\end{itemize}

\item JOSS Peer Review & rOpenSci onboarding
\begin{itemize} 
\item \url{http://joss.theoj.org/about#reviewer_guidelines} 
\item E.g., \url{https://github.com/openjournals/joss-reviews/issues/43}
\item \url{https://github.com/ropensci/onboarding}
\item \url{http://ropensci.org/blog/2016/03/28/software-review}
\end{itemize}

\item RSE 2016 Talk:
\begin{itemize}
\item \href{http://www.rse.ac.uk/conf2016_talks#T1.1}{InterMine: Best Practices for Open Source Software}
\end{itemize}

\item ANNIS corpus linguistic analysis tool
\begin{itemize}
\item \url{http://corpus-tools.org/annis/} (humanities code)
\end{itemize}

@@

Our plans are for each of the Verify Best Practices and Metrics for Sustainable Research Software to volunteer to take on one to two projects each, and as incentive the projects that individual take on can be one they are interested in.  This would lead to an estimated 5-10 projects to be evaluated within this project.  In terms of increasing this sample size, it is our hope that once we document the workflow by which these evaluations are performed, others can be self-sufficient in following this workflow and contribute their own evaluations of software they wish to evaluate and have interest in.

@@

To join this group or obtain more information about it, please send an email to: \href{wssspe4-verify-best-practices@googlegroups.com}{Verifying best practices \& metrics for sustainable research software.}

>>>>

Many open source projects for research software document their best practices that contributed to the sustainability of the software.  Many open source projects also document software metrics they use to define their research software project's success.  This project endeavors to aggregate several sources of these best practices into a consolidated list of best practices, as and to also do the same for software metrics in another consolidated list.  Our team will then create a workflow to evaluate how open source projects stand up to these lists.

@@

The overall objective of the Verifying Best Practices and Metrics for Sustainable Software working group is to take the outputs of the WSSSPE efforts to identify best practices for creation of sustainable software for science/academia, and also the outputs of WSSSPE efforts to identify metrics for sustainable software for science/academia and cross-reference these with current open source research software that successfully uses modern software engineering.  This will allow us to identify gaps on both sides.  This approach will also allow the group to  hypothesize how successful open source projects can be further improved, verify that recommended approaches for software engineering for science/academia are sufficient and valid, and that metrics for software engineering for science/academia are relevant and useful.  The group has a specific objective of getting a good cross-sampling of disparate software including community model codes, community cyberinfrastructure, community analytic tools, etc.

@@

\noindent
Resources include research projects suggested from WSSSPE community including:
\begin{itemize}
\item FLASH (astrophysics, \url{http://flash.uchicago.edu/site/flashcode/})
\item GROMACS (chemistry, \url{http://www.gromacs.org/})
\item CIG (Earth science, \url{http://geodynamics.org/})
\item CUAHSI (Earth science, \url{https://www.cuahsi.org/})
\item CSDMS (Earth science, \url{https://csdms.colorado.edu/wiki/Main_Page})
\item OntoSoft (biology, \url{http://www.ontosoft.org/})
\item ASCL (astronomy, \url{http://ascl.net}), specifically ASCL entries sorted by citation count\footnote{\url{https://ui.adsabs.harvard.edu/\#search/q=bibstem\%3A\%22ASCL\%22&sort=citation_count\%20desc\%2C\%20bibcode\%20desc}}
\item yt-project (astronomy,  \url{http://yt-project.org})
\item Einstein Toolkit (physics, \url{https://einsteintoolkit.org/})
\item SpEC (physics, \url{https://www.black-holes.org/SpEC.html})
\item pyCLOUDY (astrophysics, \url{http://ascl.net/1304.020})
\end{itemize}

@@

\begin{itemize}

\item Good Enough Practices in Scientific Computing, Wilson et al. 2016~\cite{DBLP:journals/corr/WilsonBCKNT16}
\begin{itemize}
\item \url{https://swcarpentry.github.io/good-enough-practices-in-scientific-computing/}
\end{itemize}

\item Best Practices for Scientific Computing, Wilson et al. 2014~\cite{bestprSC}
\begin{itemize}
\item 8 high level categories 
\end{itemize}

\item Butterfly: a paradigm towards stable bio and neuro informatics tools development~\cite{10.3389/conf.fnins.2015.91.00009}

@@

%same as 2nd in list
%\item Best Practices for Scientific Computing
%\begin{itemize}
%\item \url{http://arxiv.org/abs/1210.0530v1}
%\end{itemize}

@@

\item WSSSPE papers from past WSSSPE workshops
\begin{itemize}
\item \url{http://wssspe.researchcomputing.org.uk/}
\item published as JORS collection (\url{http://openresearchsoftware.metajnl.com/collections/special/working-towards-sustainable-software-for-science/})
\end{itemize}

\item JOSS Peer Review and rOpenSci onboarding
\begin{itemize} 
\item \url{http://joss.theoj.org/about#reviewer_guidelines} 
\item Example JOSS review: \url{https://github.com/openjournals/joss-reviews/issues/43}
\item \url{https://github.com/ropensci/onboarding}
\item \url{http://ropensci.org/blog/2016/03/28/software-review}
\end{itemize}

\item RSE 2016 Talk:
\begin{itemize}
\item InterMine: Best Practices for Open Source Software (\url{http://www.rse.ac.uk/conf2016_talks#T1.1})
\end{itemize}

\item ANNIS corpus linguistic analysis tool
\begin{itemize}
\item humanities code (\url{http://corpus-tools.org/annis/})
\end{itemize}

@@

Our plans are for each of the Verify Best Practices and Metrics for Sustainable Research Software to volunteer to take on one to two projects each, and as incentive the projects that individual take on can be one they are interested in.  This would lead to an estimated 5--10 projects to be evaluated within this project.  In terms of increasing this sample size, it is our hope that once we document the workflow by which these evaluations are performed, others can be self-sufficient in following this workflow and contribute their own evaluations of software they wish to evaluate and have interest in.

@@

To join this group or obtain more information about it, please send an email to the Verifying best practices \& metrics for sustainable research software group: <wssspe4-verify-best-practices@googlegroups.com>.

### 2017-04-09 WSSSPE4_report/wg_best_practices_undergrads.tex

The participants in this working group are/were Jonah Miller,
Aleksandra Nenadic, Raniere Silva, Francisco Queiroz, Hans Fangohr,
and Prabhjyot Sing. Aleksandra Nenadic and Raniere Silva are involved
in software and data carpentry.

>>>>

\begin{itemize}
  \item Jonah Miller <jmiller@perimeterinstitute.ca>
  \item Aleksandra Nenadic <a.nenadic@manchester.ac.uk>
  \item Raniere Silva <raniere.silva@software.ac.uk>
  \item Francisco Queiroz <chico@puc-rio.br>
  \item Hans Fangohr <fangohr@soton.ac.uk>
  \item Prabhjyot Sing <prabhjyot10@gmail.com>
\end{itemize}

\noindent Aleksandra Nenadic and Raniere Silva are involved
in software and data carpentry.

### 2017-04-09 WSSSPE4_report/wg_codemeta.tex

"Define a standard for metadata to be used in current repos including authors, dependencies, ... repo url" had been listed as a possible project for a working group; as several attendees have been participating in a project, CodeMeta,\footnote{\url{http://codemeta.github.io/}} that is currently working on software metadata, an enthusiastic group formed to work on advancing the CodeMeta project.

@@

\begin{itemize}
\item Gabrielle Allen <gdallen@illinois.edu>
\item Stephan Druskat <stephan.druskat@hu-berlin.de>
\item Iain Emsley <iain.emsley@oerc.ox.ac.uk>
\item Carole Goble <carole.goble@manchester.ac.uk>
\item Chris Gwilliams <gwilliamsc@cardiff.ac.uk>
\item Rafael Jimenez <rafael.jimenez@elixir-europe.org>
\item Frank Löffler <knarf@cct.lsu.edu>
\item Kyle Niemeyer <Kyle.Niemeyer@oregonstate.edu>
\item Thomas Robitaille <thomas.robitaille@gmail.com>
\item Rob Welch <py12rw@leeds.ac.uk>
\item Alice Allen <aallen@ascl.net>
\end{itemize}

@@

The primary objective of this working group was to find ways to help the CodeMeta project come to fruition. CodeMeta seeks in part to create a "Rosetta Stone" for software metadata to facilitate retaining such metadata between repositories, services, registries, indexers, publishers, citation managers, and other entities that create, ingest, use, and/or store metadata about software. The project also wants to establish a JSON-LD schema as a tool for making metadata machine-readable.\citep{CodeMeta_schema}

@@

\begin{itemize}
\item {\bf Carl Boettiger}, UC Berkeley
\item {\bf Matt Jones}, NCEAS
\item {\bf Arfon Smith}, GitHub
\item {\bf Abby Mayes}, Mozilla Science Lab
\item Yolanda Gil, USC ISI
\item Peter Slaughter, NCEAS
\item Patricia Cruse, DataCite
\item Neil Chue Hong SSI
\item Mercè Crosas, Harvard IQSS
\item Martin Fenner, DataCite
\item Mark Hahnel, figshare
\item Luke Coy, RIT & MSL
\item {\em Kyle Niemeyer}, Oregon State
\item Krzysztof Nowak, Zenodo
\item Daniel Katz, NCSA
\item {\em Carole Goble}, University of Manchester
\item Ashley Sands, UCLA
\item {\em Alice Allen}, ASCL

@@

Other resources to draw on are the software metadata vocabularies of Schema.org (\url{https://schema.org/SoftwareSourceCode}) and DOAP (\url{https://github.com/ewilderj/doap}), and the Force11 Software Citation Principles\citep{Smith:2016sc}. Relevant documents on research software, including the Guidelines for persistently identifying software using DataCite\citep{Gent2016} are available on the UK's Research Data Network's Research Software web page (\url{https://research-data-network.readme.io/docs/research-software}).

@@

Our plans are for the working group to engage with those already working on CodeMeta, to examine the existing CodeMeta crosswalk table to see what improvements and additions might be made, and to determine how to engage the community and provide ongoing social engagement and structure. Further, the group wants to assist in the implementation of the specifications and, by providing an outsider’s view, contribute suggestions for more understandable project documentation. Finally, the WG seeks a better way or ways to present the crosswalk table to make it more easily understood and consumable by research software communities.

>>>>

This group, which included people who had previously been working on the CodeMeta project\footnote{\url{http://codemeta.github.io/}}, formed to address the proposed project,
 ``Define a standard for metadata to be used in current repos including authors, dependencies, ... repo url.''

@@

\begin{itemize}
\item Gabrielle Allen <gdallen@illinois.edu>
\item Stephan Druskat <stephan.druskat@hu-berlin.de>
\item Iain Emsley <iain.emsley@oerc.ox.ac.uk>
\item Carole Goble <carole.goble@manchester.ac.uk>
\item Chris Gwilliams <gwilliamsc@cardiff.ac.uk>
\item Rafael Jimenez <rafael.jimenez@elixir-europe.org>
\item Frank L\"{o}ffler <knarf@cct.lsu.edu>
\item Kyle Niemeyer <Kyle.Niemeyer@oregonstate.edu>
\item Thomas Robitaille <thomas.robitaille@gmail.com>
\item Rob Welch <py12rw@leeds.ac.uk>
\item Alice Allen <aallen@ascl.net>
\end{itemize}

@@

The primary objective of this working group was to find ways to help the CodeMeta project come to fruition. CodeMeta seeks in part to create a ``Rosetta Stone'' for software metadata to facilitate retaining such metadata between repositories, services, registries, indexers, publishers, citation managers, and other entities that create, ingest, use, and/or store metadata about software. The project also wants to establish a JSON-LD schema as a tool for making metadata machine-readable~\cite{CodeMeta_schema}.

@@

\begin{itemize}
\item {\bf Carl Boettiger}, UC Berkeley
\item {\bf Matt Jones}, NCEAS
\item {\bf Arfon Smith}, Space Telescope Science Institute
\item {\bf Abby Mayes}, Mozilla Science Lab
\item Yolanda Gil, USC ISI
\item Peter Slaughter, NCEAS
\item Patricia Cruse, DataCite
\item Neil Chue Hong SSI
\item Merc\`{e} Crosas, Harvard IQSS
\item Martin Fenner, DataCite
\item Mark Hahnel, figshare
\item Luke Coy, RIT \& MSL
\item {\em Kyle Niemeyer}, Oregon State
\item Krzysztof Nowak, Zenodo
\item Daniel S. Katz, NCSA
\item {\em Carole Goble}, University of Manchester
\item Ashley Sands, UCLA
\item {\em Alice Allen}, ASCL

@@

Other resources to draw on are the software metadata vocabularies of Schema.org\footnote{\url{https://schema.org/SoftwareSourceCode}} and DOAP\footnote{\url{https://github.com/ewilderj/doap}}, and the FORCE11 Software Citation Principles~\cite{Smith:2016sc}. Relevant documents on research software, including the Guidelines for persistently identifying software using DataCite~\cite{Gent2015} are available on the UK's Research Data Network's Research Software web page\footnote{\url{https://research-data-network.readme.io/docs/research-software}}.

@@

Our plans are for the working group to engage with those already working on CodeMeta, to examine the existing CodeMeta crosswalk table to see what improvements and additions might be made, and to determine how to engage the community and provide ongoing social engagement and structure. Further, the group wants to assist in the implementation of the specifications and, by providing an outsider's view, contribute suggestions for more understandable project documentation. Finally, the WG seeks a better way or ways to present the crosswalk table to make it more easily understood and consumable by research software communities.

### 2017-04-09 WSSSPE4_report/wg_letters.tex

Alice Allen, Astrophysics Source Code Library, \url{aallen@ascl.net};
Gabrielle Allen, NCSA, \url{University of Illinois, gdallen@illinois.edu};
Wolfgang Bangerth, Colorado State University, \url{bangerth@colostate.edu};
Bruce Childers, University of Pittsburgh, \url{childers@cs.pitt.edu };
Lorraine Hwang, University of California, \url{Davis, ljhwang@ucdavis.edu };
Dan Katz, University of Illinois, \url{dskatz@illinois.edu };
Frank L{\"o}ffler, Louisiana State University, \url{knarf@cct.lsu.edu};
Kyle Niemeyer, Oregon State University, \url{kyle.niemeyer@oregonstate.edu};
Janos Sallai, Vanderbilt University, \url{janos.sallai@vanderbilt.edu }.

>>>>

\begin{itemize}
\item Alice Allen <aallen@ascl.net>
\item Gabrielle Allen <gdallen@illinois.edu>
\item Wolfgang Bangerth <bangerth@colostate.edu>
\item Bruce Childers <childers@cs.pitt.edu>
\item Lorraine Hwang <ljhwang@ucdavis.edu>
\item Daniel S. Katz <d.katz@ieee.org>
\item Frank L{\"o}ffler <knarf@cct.lsu.edu>
\item Kyle Niemeyer <Kyle.Niemeyer@oregonstate.edu>
\item Janos Sallai <janos.sallai@vanderbilt.edu>
\end{itemize}

### 2017-04-09 WSSSPE4_report/wg_metrics.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{White paper on developing sustainable softwares}
\label{sec:best-practices-developing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\note{Sandra to write this}

Introduction to group here, including the overall objective of work in this area.

@@

members of the working group

@@

Specific things the working group wants to accomplish in the context of the larger objective.

@@

What is the gap or challenge being addressed?

@@

What people, groups, or resources are needed.

@@

What tasks will the working group undertake

@@

What are the first SMART steps proposed?

@@

How could a reader get more information or get more involved?

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Meaningful metrics for sustainable software}
\label{sec:metrics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\note{content from Emily}

%Introduction to group here, including the overall objective of work in this area.

Meaningful Metrics for Sustainable Scientific Software aims to increase the visibility on the quality of scientific software, facilitate the reusability of scientific software, and promote the best software practices by standardizing metrics via interviews with scientific software developers. This working group believes improving the current software metrics system will increase software sustainability. Currently, there are inefficiencies regarding software duplication, sustainability, and selection, as well as others, within the scientific software community. In order to address these inefficiencies, Meaningful Metrics for Sustainable Scientific Software aims to create a goal-oriented method to collecting productive metrics by focusing on the developer side of software.

@@

%members of the working group

\begin{itemize}
\item Emily Chen <echen35@illinois.edu>
\item Patricia Lago <pdotlago@gmail.com>
\item Udit Nangia <unangi2@illinois.edu>
\item Tengyu Ma <tengyuma10717@gmail.com>
\item Aseel Aldabjan <a.dabjan@hotmail.com>
\end{itemize}

@@

%Specific things the working group wants to accomplish in the context of the larger objective.

In the context of the larger objective, Meaningful Metrics for Sustainable Scientific Software hopes to find an efficient solution for streamlining the process of collecting and utilizing metrics to benefit software sustainability, as well as minimize the current inefficiencies within the scientific software community. Finding meaningful metrics will improve software evaluation and comparison, thus reducing the effort spent on seeking scientific software.

@@

%What is the gap or challenge being addressed?

The gap being addressed is the lack of a standard for collecting and presenting metrics. This gap delays workflow and creates a multitude of tedious tasks, including searching for the best-fit software, unknowingly duplicating software, and other related busy-work. The need for metric standardization stems from the abundance of scientific, both ?dark? and open source, software and the difficulties of ensuring the software is sustainable.

@@

%What people, groups, or resources are needed.

Relevant people and resources include scientific software developers, researchers that use scientific software, scientific software funding institutions.

@@

%What tasks will the working group undertake

This working group plans on interviewing scientific software developers to form metrics from the goals they have for their software.

@@

%What are the first SMART steps proposed?

The SMART steps Meaningful Metrics for Scientific Software has proposed are:
\begin{enumerate}
\item Identify the population of scientific software developers who are willing to be interviewed
\item Define the interview questions and organize them into categories
\item Interview the participants and map the survey results on goals
\item Convert the goals to feasible, meaningful metrics
\item Analyze the collected metrics
\end{enumerate}

@@

%How could a reader get more information or get more involved?

For more information, please contact Emily Chen at <echen35@illinois.edu>.

### 2017-04-09 WSSSPE4_report/wg_open_research_index.tex

The members of this group at WSSSPE4 were:
Gabrielle Allen,
Bruce Childers,
Robert Haines,
Caroline Jay,
Dan Katz,
Robert McDonald,
Daniel Mosse,
and 
Kyle Niemeyer.

>>>>

\begin{itemize}
\item Gabrielle Allen <gdallen@illinois.edu>
\item Bruce Childers <childers@pitt.edu>
\item Robert Haines <robert.haines@manchester.ac.uk>
\item Caroline Jay <caroline.jay@manchester.ac.uk>
\item Daniel S. Katz <d.katz@ieee.org>
\item Robert McDonald <rhmcdona@indiana.edu>
\item Daniel Mosse <mosse@cs.pitt.edu>
\item Kyle Niemeyer <Kyle.Niemeyer@oregonstate.edu>
\end{itemize}
